Extrinsic Type Inference (DRAFT 2025-06-09)

### 2025-07-10 extrinsic_type_inference_paper/paper.tex
add packing requirements
add completeness lemmas

@@

@@

\TODO{add requirements on packing}

\TODO{add requirements on negatble checks}

>>>>

\begin{requirement}
  \label{req:positive packing correspondence}
  \emph{positive packing correspondence}
  \footnotesize
  \nopad
  \begin{mathpar}
    \inferrule {
      \textbf{pack}^+(\Theta \entails \Pi) = \tau 
      \\
      \delta \satisfies \Delta
      \\
      \Theta \subseteq \textbf{dom}(\delta)
    } {
      (\forall  \Theta^\dagger, \Delta^\dagger, \tau^\dagger \qua 
      (\Theta^\dagger, \Delta^\dagger, \tau^\dagger) \in \Pi \implies
      (
      \exists \delta^\dagger \qua \textbf{dom}(\delta^\dagger) \subseteq \Theta^\dagger \backslash \Theta \up 
      \\\\
      (
      \forall \delta' \qua 
      \textbf{dom}(\delta') \cap \textbf{ftv}(\Delta) = \emptyset \implies
      \delta \oplus \delta' \oplus \delta^\dagger \satisfies \Delta \cup \Delta^\dagger \implies
      \delta \oplus \delta' \oplus \delta^\dagger \satisfies e \hastype \tau^\dagger
      )
      ) 
      \\\\
      \iff
      \\\\
      \delta \satisfies e \hastype \tau
    }
  \end{mathpar}
\end{requirement}

\begin{requirement}
  \label{req:negative packing correspondence}
  \emph{negative packing correspondence}
  \footnotesize
  \nopad
  \begin{mathpar}
    \inferrule {
      \textbf{pack}^-(\Theta \entails \Pi) = \tau 
      \\
      \delta \satisfies \Delta
      \\
      \Theta \subseteq \textbf{dom}(\delta)
    } {
      (\exists  \Theta^\dagger, \Delta^\dagger, \tau^\dagger \qua 
      (\Theta^\dagger, \Delta^\dagger, \tau^\dagger) \in \Pi \up
      (
      \forall \delta^\dagger \qua \textbf{dom}(\delta^\dagger) \subseteq \Theta^\dagger \backslash \Theta \implies
      \\\\
      (
      \exists \delta' \qua 
      \textbf{dom}(\delta') \cap \textbf{ftv}(\Delta) = \emptyset \up
      \delta \oplus \delta' \oplus \delta^\dagger \satisfies \Delta \cup \Delta^\dagger \up
      \delta \oplus \delta' \oplus \delta^\dagger \satisfies e \hastype \tau^\dagger
      )
      ) 
      \\\\
      \iff
      \\\\
      \delta \satisfies e \hastype \tau
    }
  \end{mathpar}
\end{requirement}

@@

\begin{requirement}
  \label{req:proof_subtyping_sequence_completeness_under_negatability}
  \emph{proof subtyping sequence completeness under negatability} 
  \small
  \nopad
  \begin{mathpar}
    \inferrule {
      \Theta, \Delta \Vvdash \Omega
      \\
      \Theta, \Delta \entails \Omega \given \Theta', \Delta'
      \\
      \delta' \satisfies \Delta'
    } {
      \forall \delta^\dagger \qua
      \delta' \oplus \delta^\dagger \satisfies \Omega \implies
      \delta' \oplus \delta^\dagger \satisfies \Delta'
    }
  \end{mathpar}
\end{requirement}

\begin{requirement}
  \label{req:proof subtyping completeness under negatability}
  \emph{proof subtyping completeness under negatability}  
  \small
  \nopad
  \begin{mathpar}
    \inferrule {
      \Theta, \Delta \Vvdash \eta
      \\
      \Theta, \Delta \entails \tau \subtypes \eta \given \Theta', \Delta'
      \\
      \delta' \satisfies \Delta'
    } {
      \forall \delta^\dagger \qua
      \delta' \oplus \delta^\dagger \satisfies \tau \subtypes \eta \implies
      \delta' \oplus \delta^\dagger \satisfies \Delta'
    }
  \end{mathpar}
\end{requirement}

\begin{requirement}
  \label{req:proof subtyping existential completeness under negatability}
  \emph{proof subtyping existential completeness under negatability}  
  \small
  \begin{mathpar}
    \inferrule {
      \Theta, \Delta \Vvdash \eta
      \\
      \delta \satisfies \tau \subtypes \eta
      \\
      \delta \satisfies \Delta
    } {
      \exists \Theta', \Delta' \qua \Theta, \Delta \entails \tau \subtypes \eta \given \Theta', \Delta'
    }
  \end{mathpar}
\end{requirement}

@@
